Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-03-04 demystify.tex
updates

% \section{Preparing and Tracking Applications}

@@

Students, especially international ones, often get confused on what to do after they get an offer from a professor, e.g., how to postpone or accept/reject offers, and most importantly, how to do so without offending anyone. In short, if you are not serious about an offer for any reason (e.g., still waiting for other offers), do not accept it.
If you are not sure, ask for more time to decide.  But do not accept an offer and then later reject it.  This is considered \emph{rude and unprofessional}, and will likely burn bridges with that prof.

>>>>

\paragraph{Follow Up Emails} If you had an interview and have not heard back, you can send an email to ask about the status of your application Don't send this too soon though, perhaps wait at least 2 weeks.

You can also send an email to ask about the status of your application if you have received offers from other schools and need to make a decision soon. See \autoref{sec:accept-postpone-decline} for how to accept/postpone/decline offers.
% \section{Preparing and Tracking Applications}

@@

Students, especially international ones, often get confused on what to do after they get an offer from a professor, e.g., is it OK to postpone or accept/reject offers, and most importantly, how to do so without offending anyone. Many wonder about accepting an offer and then later rejecting it.  This section provides some guidance on these issues.

In short, if you are not serious about an offer for any reason (e.g., still waiting for other offers), do not accept it.
If you are not sure, ask for more time to decide.  But do not accept an offer and then later reject it.  This can be considered \emph{rude and unprofessional}, and will likely burn bridges with that prof.
